Fixing Vulnerabilities Hinders Maintainability

### 2020-04-09 paper/icsme20.tex

vulnerabilities in software maintenance across open-source software.

@@

maintainability, we resort on Software Improvement Group (SIG)'s web-based source 

@@

are based in the OWASP Top $10$ of $2013$~\cite{oswap:2013} and OWASP Top $10$ of

@@

Our approximation was calculated using an initial step of $1$. Every $10$ attempts to search for 
a change with the same \emph{diff} the step increased. Thus, if a change suffered $20$ deletions 
and $10$ additions. Then, in the first $10$ attempts, the algorithm searches for a \emph{diff} with 
deletions between $19$ and $21$ and additions between $9$ and $11$. After the $10$ first attempts, 
the algorithm increase the step for $2$ and searches for a \emph{diff} with deletions between $18$ and $22$ and additions between 
$8$ and $10$. We originate the regular commits from the security
commits to ensure that differences in maintainability are not a consequence of
characteristics of different projects.

@@

Figure~\ref{fig:bchrep} shows an example of the report
provided by BCH for a project after finishing its evaluation. The example
refers to the OpenSSL CVE-$2014$-$3506$ vulnerability refactoring ---
as described as motivating example in Section~\ref{sec:motivation}. This
version of OpenSSL only complies with $1$ out of $10$ guidelines: \emph{Write
Clean Code}.

@@

Regarding security commits results, we observe that maintainability decreases in
$41.76\%$ ($433$), remains the same in $19.67\%$ ($204$) and increases in $38.57\%$
($400$) of the cases after security patches are applied. The resulting
p-value of the Paired Wilcoxon signed-rank test is $4.78$x$10^{-2}$.
Since the p-value is below the significance level of $0.05$, we argue that
\emph{security patches have a negative impact in the maintainability of
open-source software}.
Regarding the impact of security patches for each guideline, we observe
that overall patches have a significant positive impact in $5$ guidelines: 
\emph{Write Clean Code} (p-value = $4.9$x$10^{-54}$), \emph{Keep Architecture 
Components Balanced} (p-value = $5.26$x$10^{-71}$), \emph{Couple Architecture 
Components Loosely} (p-value = $2.43$x$10^{-07}$), \emph{Keep Unit Interfaces 
Small} (p-value = $2.25$x$10^{-13}$), \emph{ Write Code Once} (p-value = 
$7.9$x$10^{-35}$). However, for each of these guidelines we also observe a substantial number of cases where the maintainability suffers a negative impact $-$ from $10\%$ to $35\%$ $-$ which highlights the need of better practices/techniques/tools to produce software. \emph{Separate Concerns in Module} 
guideline also follows the same results but without any statistical 
significance since the p-value is higher than $0.05$. According to the 
results, \emph{Write Simple Units of Code} (p-value=$0.015$ and $38.2\%$/$396$ 
of negative cases) and \emph{Write Short Units of Code} (p-value=$0.029$ and 
$38.3\%$/$397$ of negative cases) are the most affected affected guidelines.

>>>>

vulnerabilities on software maintenance across open-source software.

@@

maintainability, we resort to Software Improvement Group (SIG)'s web-based source 

@@

are based on the OWASP Top $10$ of $2013$~\cite{oswap:2013} and OWASP Top $10$ of

@@

Our approximation was calculated using an initial step of $1$. Every $10$ attempts to search for 
a change with the same \emph{diff} the step increased. Thus, if a change suffered $20$ deletions 
and $10$ additions, then, in the first $10$ attempts, the algorithm searches for a \emph{diff} with 
deletions between $19$ and $21$ and additions between $9$ and $11$. After the $10$ first attempts, 
the algorithm increase the step for $2$ and searches for a \emph{diff} with deletions between $18$ and $22$ and additions between 
$8$ and $10$. We originate the regular commits from the security
commits to ensure that differences in maintainability are not a consequence of
characteristics of different projects.

@@

Figure~\ref{fig:bchrep} shows an example of the report
provided by BCH for a project after finishing its evaluation. The example
refers to the OpenSSL CVE-$2014$-$3506$ vulnerability refactoring ---
as described by Section~\ref{sec:motivation}. This
version of OpenSSL only complies with $1$ out of $10$ guidelines: \emph{Write
Clean Code}.

@@

Regarding security commits results, we observe that maintainability decreases in
$41.76\%$ ($433$), remains the same in $19.67\%$ ($204$) and increases in $38.57\%$
($400$) of the cases after security patches are applied. The resulting
p-value of the Paired Wilcoxon signed-rank test is $4.78$x$10^{-2}$.
Since the p-value is below the significance level of $0.05$, we argue that
\emph{security patches have a negative impact on the maintainability of
open-source software}.
Regarding the impact of security patches for each guideline, we observe
that overall patches have a significant positive impact in $5$ guidelines: 
\emph{Write Clean Code} (p-value = $4.9$x$10^{-54}$), \emph{Keep Architecture 
Components Balanced} (p-value = $5.26$x$10^{-71}$), \emph{Couple Architecture 
Components Loosely} (p-value = $2.43$x$10^{-07}$), \emph{Keep Unit Interfaces 
Small} (p-value = $2.25$x$10^{-13}$), \emph{ Write Code Once} (p-value = 
$7.9$x$10^{-35}$). However, for each of these guidelines we also observe a substantial number of cases where the maintainability suffers a negative impact $-$ from $10\%$ to $35\%$ $-$ which highlights the need of better practices/techniques/tools to produce software. \emph{Separate Concerns in Module} 
guideline also follows the same results but without any statistical 
significance since the p-value is higher than $0.05$. According to the 
results, \emph{Write Simple Units of Code} (p-value=$0.015$ and $38.2\%$/$396$ 
of negative cases) and \emph{Write Short Units of Code} (p-value=$0.029$ and 
$38.3\%$/$397$ of negative cases) are the most affected affected guidelines.
